---
output: html_document
params:
  imported: NA
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

---
title: `r params$imported$title`
---

Description: `r params$imported$description`


## 0 Standard QC plots for batch effect

- sample mean line graph, boxplot, and PCA graph
- hierarchical clustering on batch effect
- heatmap on batch effect

```{r}
library(gridExtra)
if (!is.null(params$imported$QCeffectPlott)){
grid.arrange(grobs=params$imported$QCeffectPlot[["plot"]])
params$imported$QCeffectPlot[["clustering"]]
params$imported$QCeffectPlot[["heatmap"]]}
```

## 1 Sample-based quality control plots

- %CV violin plot
- %CV stacked bar chart
- Bar chart of # available proteins in each sample, colored by group
- Upset plot shows overlap of available proteins across groups
- Data completeness
- Pearson and Spearman correlation plot

```{r}
params$imported$cvviolin
params$imported$cvstacked
params$imported$distprotein
params$imported$upset
params$imported$datacompleteness
params$imported$corplot
```

## 2 Pre-processing
Violin plot of protein intensities of all samples after pre-processing steps.
```{r}
printprocessing<-function(x){
  print(paste0("Displaying violin plot and summary for ", x))
  params$imported[[paste0("viewviolin_for_",x)]]
  params$imported[[paste0("viewsummary_for_",x)]]
}
lapply(params$imported$available_sets, printprocessing)
```

## 3 Statistical inference
Volcano plot of differential expression tests. 
```{r}
params$imported$volcanoplot
```

## 4 Dimension reduction
```{r}
params$imported$dmr
```

## 5 Clustering
```{r}
params$imported$clustering
```

## 6 Individual Protein Visualization
- boxplot of feature you chose
```{r}
params$imported$IDV_boxplot
```

- correlation plot between features
```{r}
params$imported$IDV_corrplot
params$imported$IDV_corrtable
```

- protein structure plot
```{r}
ind<-names(params$imported)[grep("CLG_for_",names(params$imported))]
if (length(ind)>0){
lapply(ind, function(x) params$imported[[x]])}
```

- circosplot
```{r}
params$imported$circosplot
```

# Reference 
[link]shiny app 