---
title: "Report by"
output: html_document
params:
  imported: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## 1 Sample-based quality control plots
- %CV violin plot
- %CV stacked bar chart
- Bar chart of # available proteins in each sample, colored by group
- Upset plot shows overlap of available proteins across groups
- Data completeness
- Pearson and Speerman correlation plot

```{r}
params$imported$cvviolin
params$imported$cvstacked
params$imported$distprotein
params$imported$upset
params$imported$datacompleteness
params$imported$corplot
```

## 2 Pre-processing
Violin plot of protein intensities of all samples after pre-processing steps.

```{r}
params$imported$violinplot
```

## 3 Statistical inference
### 3.1 Equivalence test
```{r}
if (exists("eqtest1", params$imported)){
  params$imported$eqtest1}
if (exists("eqtest2", params$imported)){
  params$imported$eqtest2}
```

### 3.2 Differential expression test
Volcano plot of differential expression tests. 
```{r}
params$imported$volcanoplot
```

## 4 Dimension reduction
```{r}
params$imported$dmr
```

## 5 Clustering
```{r}
params$imported$clustering
```

# Reference 
[link]shiny app 